Pushdown Control-Flow Analysis via Refunctionalization (Functional Pearl)

### 2018-03-11 paper.tex
update abstract

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  Abstracting abstract machines (AAM) is a systematic methodology 
  for constructing abstract interpreters that derived from concrete
  small-step abstract machines. Recent progress applies the same idea 
  on definitional interpreter and obtains a big-step 
  abstracting definitional interpreter (ADI) written in monadic style.
  Danvy shows the correspondence between concrete abstract machines and interpreters.
  Yet, the relations between small-step abstracting abstract machines and 
  big-step abstracting definitional interpreters is not well studied.

  In this paper, we show their correspondence and how to syntactically transform small-step 
  abstracting abstract machines into big-step abstracting definitional 
  interpreters.
  The transformations include fusing, disentangling, refunctionalizing 
  and monadification (or un-CPS to direct-style with delimited continuations). 
  All of them properly handle the 
  collecting semantics and the non-determinism of abstract interpretation. 
  After each transformation, we also obtain an intermediary form of 
  abstract interpreter.
  Remarkably, refunctionalization sequentializes the abstract evaluation.
  And follow the idea that evaluation contexts are defunctionalized 
  continuations, we reveal how precise call/return match in control-flow 
  analysis can be obtained by refunctionalizing a small-step abstract interpreter.
  as well as explain how it been lost by defunctionalizing the higher-order
  continuations into an firts-order data type.

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  Abstracting abstract machines (AAM) is a systematic methodology 
  for constructing abstract interpreters that are derived from concrete
  small-step abstract machines. Recent progress applies the same idea 
  on definitional interpreter and obtains big-step 
  abstracting definitional interpreters (ADI) written in monadic style.
  Danvy shows the correspondence between concrete abstract machines and interpreters.
  Yet, the relations between small-step abstracting abstract machines and 
  big-step abstracting definitional interpreters is not well studied.

  In this paper, we show their correspondence and how to syntactically transform small-step 
  abstracting abstract machines into big-step abstracting definitional 
  interpreters.
  The transformations include fusing, disentangling, refunctionalizing 
  and monadification (or un-CPS to direct-style with delimited continuations). 
  All of them properly handle the 
  collecting semantics and the non-determinism of abstract interpretation. 
  After each transformation, we also obtain an intermediary form of 
  abstract interpreter.

  Remarkably, refunctionalization sequentializes the abstract evaluation.
  Following the idea that evaluation contexts are defunctionalized 
  continuations, we reveal how precise call/return match in control-flow 
  analysis can be obtained by properly refunctionalizing a small-step abstract interpreter.
  As well as we explain how it been lost by defunctionalizing the higher-order
  continuations into an first-order data type.
